Atomify - a live LAMMPS visualizer

### 2017-03-04 ms.tex
Mention Atomify mobile

>>>>

A simplified version of Atomify is made available for mobile platforms (Android
and iOS).
This version of Atomify provides access to some of the examples and is intended
for exploration of molecular dynamics simulations by students.
It also works as a demonstration of the visualization capabilities of the
desktop version of the software.
The authors are optimistic that teachers can use the visualizations provided by
Atomify to explain microscopic interactions underlying concepts in topics such
as thermodynamics, geophysics, and biology.
